Probability

### 2016-04-27 prob.tex
typos

The mathematical framework above assumes that one has complete
knowledge of the events and their relationships. However, in many
practical situations, the structure of the event space is only
partially known and the precise dependence of two events on each other
cannot, a priori, be determined with certainty. In the quantum case,
this partial knowledge is compounded by the fact that there exist
non-commuting events which cannot happen simultaneously. To
accommodate these more complex situations, we abandon the sample
space~$\Omega$ and reason directly about events. A quantum probability
space therefore consist of just two components: a set of events
$\qevents$ and a probability measure
$\mu : \qevents \rightarrow [0,1]$. We give an example before giving
the formal definition.

@@

\begin{definition}[Projection Operators; Orthogonality; Commutativity]
  Given a Hilbert space $\Hilb$, a projection operator $P$ is a linear
  transformation from $\Hilb$ to itself such that $P^2 = P$. An
  orthogonal projection furthermore satisfies $P = P^*$. Projection
  operators have the following properties:
\begin{itemize}
\item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
  P_2P_1 = \mathbb{0}$;
\item Projection operators $P_1$ and $P_2$ commute if $P_1P_2 =
  P_2P_1$;
\item If the projections $P_1$ and $P_2$ are orthogonal then f $P_1 +
  P_2$ is also a projection;
\item If the projections $P_1$ and $P_2$ commute then $P_1P_2$ is also
  a projection; it is not sufficient in this case for $P_1$ and $P_2$
  to be orthogonal. 
\end{itemize}
\end{definition}

>>>>

The mathematical framework above assumes that one has complete
knowledge of the events and their relationships. However, in many
practical situations, the structure of the event space is only
partially known and the precise dependence of two events on each other
cannot, a priori, be determined with certainty. In the quantum case,
this partial knowledge is compounded by the fact that there exist
non-commuting events which cannot happen simultaneously. To
accommodate these more complex situations, we abandon the sample
space~$\Omega$ and reason directly about events. A quantum probability
space therefore consists of just two components: a set of events
$\qevents$ and a probability measure
$\mu : \qevents \rightarrow [0,1]$. We give an example before giving
the formal definition.

@@

\begin{definition}[Projection Operators; Orthogonality;
Commutativity~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
Given a Hilbert space $\Hilb$, a projection operator $P$ is a linear transformation from $\Hilb$
to itself such that $P^2 = P = P^{\dagger}$. Projection operators have the
following properties:\footnote {``Projection'' is sometimes called
``orthogonal projection" or ``self-adjoint projection" to
emphasize $P^{\dagger} = P$~\cite{Maassen2010}.}
\begin{itemize}
\item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
  P_2P_1 = \mathbb{0}$;
\item Projection operators $P_1$ and $P_2$ commute if $P_1P_2 =
  P_2P_1$;
\item If the projections $P_1$ and $P_2$ are orthogonal then $P_1 +
  P_2$ is also a projection;
\item If the projections $P_1$ and $P_2$ commute then $P_1P_2$ is also
  a projection; it is not sufficient in this case for $P_1$ and $P_2$
  to be orthogonal. 
\end{itemize}
\end{definition}
